A new breeding crossover approach for evolutionary algorithms

### 2023-09-21 paper.tex
Functions F6 to F10 update.

>>>>

    Below, we describe the results shown in Figure~\ref{fig.experiment_F6-F10}, which includes Functions 6 through 10 (F6 to F10).

    \begin{itemize}
        \item In function F6 for the category of 10 dimensions, there was not enough evidence to determine that any of the proposals were better, while for the variety of 30, for the first occasion, the OPx alternative surpassed our CRx proposal in the statistical test.
        \item For function F7, for the category of 10 dimensions, once again, the CRx strategy outperforms its alternative through the statistical test, while for the 30-dimension type, we found not enough evidence to declare any of them as the best proposal.
        \item For function F8, for both categories, 10 and 30 dimensions, the CRx strategy found better results than the OPx alternative, passing the statistical test in both cases.
        \item For function F9, for both categories, 10 and 30 dimensions, the CRx strategy found better results than the OPx alternative, passing the statistical test in both cases.
        \item For function F10, the opposite of the previous function occurred, where for both dimensions, 10 and 30, the classic OPx strategy obtained better results than our CRx proposal by passing the statistical test in both cases.
    \end{itemize}
